---
title: "Assignment"
author: "Jake Snyder"
date: "2023-08-22"
output: github_document
---

```{r}
knitr::opts_chunk$set(echo=TRUE)
```


```{r}
library(devtools)
library(raster)
library(habtools)
library(ggplot2)
library(dplyr)
library(fishualize)

plot(horseshoe)
```

### Current lab:
Dr. Lisa McManus' Marine Ecological Theory Lab

### Project focus:
Modeling the effect of sedimentation on herbivorous fish behavior and feeding and their implications in coral-algal phase shifts.

### Why I chose this course:
This course connects organism traits with ecosystem functions, which is a central theme in my Ph.D. research. Additionally, MBIO640 teaches necessary skills that will apply to my future project, such as collecting field data to parameterize models and analyze in R.

### What do I want to learn about the most in this course:
I want to learn about 3D modeling the most, specifically laser scanning and 3D printing. I am also excited for the "Functions" module, which seems to bridge geometry and allometry with ecosystem functions.

### My R experience:
Beginner-intermediate. I have had two modeling-heavy internships: one primarily in R, and one in MatLab.

### Fun fact:
I graduated from my undergraduate institution, Penn State, with a minor in art.

